### 2018-05-21 Maths Notes/Statistics/S3/Cheat Sheet/S3 Cheat Sheet.tex
Distribution update to include discrete

\subsubsection{Continuous uniform distribution}
Remember when testing for a uniform distribution to state that it is a \textbf{continuous} uniform distribution

>>>>

\subsubsection{Uniform distributions}
It is necessary to state the type of uniform distribution:
\item \textbf{Continuous} - Can take any of the values over the range
\item \textbf{Discrete} - Can only take specific values over the range (for example odd numbers)
